\documentclass{my_cv_bis}
\hypersetup{
	}
 
\begin{document}
\heading{Antoine}{de Roquemaurel}{Developer}
 {
	\contact{
		7 impasse André Lartigue\\
		Bat. F2, Appt 41\\
		31500 Toulouse
	}{
		\mobile{+336~84~33~52~93}\\
		\email{\texttt{\href{mailto:antoine.roquemaurel@gmail.com}{\color{white}{antoine.roquemaurel@gmail.com}}}}\\
		\texttt{\hspace{-50px}\Mundus~\href{https://antoinederoquemaurel.github.io}{\color{white}{https://antoinederoquemaurel.github.io}}}
	}{	
		Born on 11/08/91 \\
		~
	}
}{Photo_mini}

\section{Work experiences}
\cventry{\proleft{2013~--~Today}{Freelance}{C++, Qt5, PHP, Symfony2, \LaTeX}}
	{Freelance Developer}
	{Autoentrepreneur}{Toulouse}
	{
	Software and Websites development, such as physiotherapist's software, websites to an association (\url{afmck.fr}) or a glass artisan
	(\url{valeriederoquemaurel.com}). 
	}
	{\course{More informations on \url{https://antoinederoquemaurel.github.io/\#portfolio}}}

	\cventry{\proleft{\mbox{May~--~August~2015}}{M1 internship}{UML, Java, Python}}
	{Development of an automation testing plateform}
	{Continental Automotive}{Toulouse, France}
	{
	Analyze, design and developmment of news features in the previous internship's project for the first delivery version. 
	}
	{}
	\cventry{\proleft{April~--~July~2014}{Licence internship}{UML, Java, Antlr4}}
	{Designing of an automation testing plateform}
	{Continental Automotive}{Toulouse, France}
	{
	Designing of a tools for automatic tests. This tool should help to test the good integration of an engine control unit.
	}
	{}

	\cventry{\proleft{July 2012}{CDD}{PHP5, Mootools}}
	{Member of web developer team}
	{Memobox / 2G Technologies}{Toulouse, France}
	{Developer in a team who develop an SaaS(\textit{Software as a Service}) application for telecommunication data. I develop a
	simple communication system with providers.} {}

	\cventry{\proleft{April~--~June 2012}{DUT Internship}{PHP5, Adobe AIR}}
	{ Design of translation system}
	{Memobox / 2G Technologies}{Toulouse, France}
	{
	Development of a new translation system based on a PHP engine and a fat client for the traduction and search in database.	} {}

	\subsection{Personnal projects}
	\cventry{December of 2010, 2011 and 2012\\{\vspace{0.5mm}\small\color{gray}~ }}
	{Participation in the \textit{nuit de l'info}}
	{Université Toulouse III -- Paul Sabatier}{Toulouse, France}
	{ National competition of computer science for students of all France. The concept is the development of a web application in one single
	night.} 
	{\course{\url{http://nuitdelinfo.com}}}
	\vspace{-10px}
\section{Skills}
%	\begin{minipage}[t]{0.45\textwidth}
		\subsection{Computer Science}
		\cvline{\textbf{Programming}}{C++, Java, C, PHP, Python, Bash, Groovy, JavaScript}
		\cvline{\textbf{Frameworks}}{Qt, Symfony2, Django, Grails, JQuery, Mootools, Bootstrap, Adobe AIR}\\
		\cvline{\textbf{Design}}{UML2, Merise}\\
		\cvline{\textbf{Versioning}}{Git, Subversion}\\
		\cvline{\textbf{DBMS}}{MySQL, SQLite, Oracle}\\
		\cvline{\textbf{Systems}}{Linux, UNIX, Windows}\\
%	\end{minipage}
%	\hfill
\vspace{-10px}
		\subsection{Languages}
		\cvline{\textbf{English}}{Technical reading and writing}
		\cvline{\textbf{French}}{Mother tongue}

\vspace{-10px}
\section{Education}
	\cventry{2014~--~2016}
	{Master in Software Engineering (Currently)}
	{Toulouse III University -- Paul Sabatier}{Toulouse}{}{}
	\cventry{2012~--~2014}
	{Licence Computer Science}
	{Toulouse III University -- Paul Sabatier}{Toulouse}{Engineering of computer systems}{}
	\cventry{2010~--~2012}
	{DUT Computer Science}
	{IUT 'A' Paul Sabatier}{Toulouse}
	{}
	{}
	\cventry{2008~--~2010}
	{Baccalauréat Sciences et Techniques de l'Industriel}
	{Saint Joseph}{Toulouse}
	{Electrical engineering}{}
	\vspace{-20px}
\section{Hobbies}
\cvline{\textbf{Associatif}}{
Member of \textit{\textbf{nuit de l'info}}'s organizers(2013, 2014)\newline 
Volunteer facilitator in Scouts and Guides of France. Children 6 to 11 (2009 -- 2012)
}
		\cvline{\textbf{Culture}}{Science fiction (Asimov) and fantastic (Tolkien) reading}

\end{document} 
